Digit Recognition Using KNN and SVM

### 2013-05-24 milestone.tex
Updating milestone writeup

\title{Exploration of Digit Recognition Algorithms}

@@

The K value that led to the lowest error rate is used to build our final classifier.

@@

TODO

>>>>

 \title{Digit Recognition Using KNN and SVM}

@@

The K value that led to the lowest error rate is used to build our final classifier. The result of our cross validation can be seen in Table 1 below.

\begin{table}[ht]
\caption{Cross Validation Selection of K} % title of Table
\centering  % used for centering table
\begin{tabular}{c c} 
\hline\hline
K & Error \\ [1.0ex]
\hline 
1 & 135 \\
2 & 164 \\
3 & 137 \\
4 & 148 \\
5 & 144 \\
10 & 163 \\
15 & 176 \\
20 & 191 \\ [1ex]
\hline
\end{tabular}
\label{table:nonlin}
\end{table}

@@

The SVM implementations we have worked with previously have involved only two classes. Because we have to classify the digits 0-9, we need to create an SVM that can classify from a broader range.

We are in the process of implementing a one-vs-one classifier. We train $n choose 2$ SVMs which compare two numbers. For example, one SVM would classify a digit as either a 1 or a 2. Another would classify a digit as a 1 or a 3, and so on. We get a prediction from all of these classifiers and take a vote to see which digit was most likely based on our SVMs.

In our training step, every time we make a mistake we log it. Future predictions are made based on past mistakes.

\begin{center}
$Classification = sign(C * \sum\limits_{m \exists Mistakes} {(Y_m * k(X_m, X))})$
\end{center}

The biggest challenge thus far has been deciding how to regularize our SVM without relying on the weights. Because we use the kernel trick, the weights are never explicitly stored.

\section{Future Work}

Our primary focus moving forward is to get our SVM implementation working. Most of the structure is in place, however we need to decide on our method of regularization. Once we have the regularization done we can analyze the effectiveness of our SVM.

For KNN it might be beneficial to attemp to increase performance. Classifying each sample takes about 1 second, and with the testing dataset holding about 50,000 samples it takes several hours to classify all the points. Possible areas of speedup are a better algorithm for finding the nearest neighbors or parallelizing the nearest neighbor search.
